---
title: "Figures' note for auditory attentional blink"
author: "Yuta Suzuki, Hsin-I Liao"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  slidy_presentation:
  # word_document:
  #    # css: style.css
  #    reference_docx: doc_templete.docx
     
params:
  year: 2026
# editor_options: 
#   markdown: 
#     wrap: 72

---

## Article information

*Corresponding author: Yuta Suzuki
NTT Communication Science Laboratories, NTT Corporation, Atsugi, Japan
Tel: +81-046-240-3525, 
E-mail:suzukiy970@gmail.com

# Results
# Experiment 1
```{r, message=FALSE, echo=FALSE,warning=FALSE,include=FALSE}

rootFolder = "/Users/yutasuzuki/Desktop/Github/"
rootFolder = "/Volumes/Burger/project/AttentinalBlink/"

expFolder = paste0(rootFolder,"AuditoryAttentionalBlink/Exp1/data")


folderName = list.files(expFolder, full.names=T)
folderName = folderName[length(folderName)]

date = unlist(strsplit(folderName,"/"))
date = date[length(date)]

dataFolder = paste0(expFolder,"AuditoryAttentionalBlink/Exp1/data/",date,"/")
saveFolder = paste0("figure/",format(Sys.time(), '%Y%m%d'),"/")

cfg = jsonlite::fromJSON(paste0(folderName,"/cfg.json"))
bpass="_015"
bpass=""

figcount = 1

sTime = cfg$TIME_START
eTime = cfg$TIME_END
analysisWin = 1
mmFlg = cfg$mmFlag

subFlg = F
nsFlag = T
saveFig = T
blinkFlg = F
normFlg = T

if(!dir.exists(saveFolder)){
  dir.create(saveFolder)
}

g2 = c('1','2','3','4','5')
g2 = c(80,160,240,320,400)

g3 = c('No-target','T1 only','T2 only','Both')
g4 = c('Behavior')

if(blinkFlg){
  g5 = c('Blink-nonsync','Blink-sync')
}else{
  g5 = c('T1-Attend','T1-Ignore','T1-Attend','T1-Ignore')
}

config <- list(lim_x = c(0,1),
               lim_y = c(2,4),
               alpha = 0.1,
               stride = 0.1,
               label_x = "Time [sec]",
               label_y = "Pupil size[a.u.]",
               title = "",
               linetype = T,
               shape=F,
               # grCol = c("#738CD9","#222222")
               # grCol = c("#AB004A","#222222")
               # grCol = c("#E69F00","#738CD9")
               grCol = c('Black','gray')
               
)

p_all = list()
anovaTable = list()

dat_exp1 <- read.xlsx(paste0(rootFolder,"AuditoryAttentionalBlink/Exp1/subInfo.xlsx"))
dat_exp2 <- read.xlsx(paste0(rootFolder,"AuditoryAttentionalBlink_realtime/subInfo.xlsx"))


df_sub = data.frame(
  exp=c(1,2),
  numOfSub = c(dim(dat_exp1)[1],dim(dat_exp2)[1]),
  numOfMen = c(length(which(dat_exp1[!is.na(dat_exp1$gender),]$gender == 'M')),
               length(which(dat_exp2[!is.na(dat_exp2$gender),]$gender == 'M'))),
  numOfWomen = c(length(which(dat_exp1[!is.na(dat_exp1$gender),]$gender == 'F')),
                 length(which(dat_exp2[!is.na(dat_exp2$gender),]$gender == 'F')))
)

```

__Attentional blink__ is a phenomenon of temporal incapable to allocate attention.
* Within a certain time window, the detection of T2 was impaired.
* Attentional resource is occupied for T1 processing, resulting a processing deficit for T2 detection.
__Distractors:__ Twenty-one 30-ms pure tones ranged from 529 to 1330 Hz
__Target 1(T1):__ Composed of six 5-ms pulses, and its frequency could be any of the 21 frequencies of the distractors
__Target 2 (T2, Probe):__ A glide that changed smoothly in frequency from 636 to 1006 Hz
* Each trial contains 20 sequence. 
* A total of 7 trials segregated with 6-s rest in-between were tested in the one session.
* Experiment included 57 % of the ‘Both’ sequence and 43 % of T1, T2 sequence.
__Task:__ Participant reported T1 and T2 sound as soon as possible when they detected them.

## Behavior
### load data
```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

df <- load_json_dataframe0(folderName, paste0("df",bpass,".json"))

```

### T1 response
```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

config$grCol = c("#E69F00","#738CD9")
config$label_x=""
config$label_y="Accuracy(T1)"

df_accuracy_T1 = df
df_accuracy_T1 = df_accuracy_T1[(df_accuracy_T1$condition=="T1_only")|(df_accuracy_T1$condition=="Both"),]
df_accuracy_T1 = df_accuracy_T1[(df_accuracy_T1$session=="T1-active"),]
df_accuracy_T1$condition = factor(df_accuracy_T1$condition, levels=g3)

df_accuracy_T1 = aggregate(hit_t1 ~ sub*condition*session, data = df_accuracy_T1, FUN = 'mean')

p_all$accuracy_T1 = dispLineGraph(df_accuracy_T1,config,"hit_t1",c('condition',"session"))+
  theme(
    legend.position = c(1,1),
    legend.justification = c(1,0)
  )

config$ylim = round(seq(0.96,1,0.01),2)
config$ylim_stride = 0.02
config$xlim = round(seq(1,2,1),2)
config$xlim_stride = 0.5

p_all$accuracy_T1 = setEmptyStyle(p_all$accuracy_T1,config)
p_all$accuracy_T1$size = c(8,10)

```

### T2 response
```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

df_accuracy_T2 = df
# df_accuracy_T2 = df_accuracy_T2[(df_accuracy_T2$target==3)|(df_accuracy_T2$target==4),]
df_accuracy_T2 = df_accuracy_T2[(df_accuracy_T2$condition=="T2_only"),]
# df_accuracy_T2$condition = g3[df_accuracy_T2$target]
# df_accuracy_T2$condition = factor(df_accuracy_T2$condition, levels=g3)

df_accuracy_T2 = aggregate(hit_t2 ~ sub*condition*session, data = df_accuracy_T2, FUN = 'mean')

config$label_y="Accuracy(T2)"
p_all$accuracy_T2 = dispLineGraph(df_accuracy_T2,config,"hit_t2",c('condition',"session"))+
  theme(
    legend.position = c(1,1),
    legend.justification = c(1,0)
  )

config$ylim = round(seq(0.9,1,0.02),2)
config$ylim_stride = 0.01
config$xlim = round(seq(1,1,1),2)
config$xlim_stride = 0.5

p_all$accuracy_T2 = setEmptyStyle(p_all$accuracy_T2,config)
p_all$accuracy_T2$size = c(4,10)

```

### P(T2|T1) response
```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

df_accuracy_T1T2 = df
df_accuracy_T1T2 = df_accuracy_T1T2[df_accuracy_T1T2$condition=="Both",]
# df_accuracy_T1T2$target = g3[df_accuracy_T1T2$target]
df_accuracy_T1T2$n=1

fit = quickpsy(df_accuracy_T1T2, lag, P.T2.T1., n, 
               grouping = c("session"), 
               prob=0.75, 
               bootstrap = "none"
               # B = 1000
)

psy_data = data.frame(
  session = fit$curves$session,
  x = fit$curves$x,
  y = fit$curves$y
)

df_accuracy_T1T2 = aggregate(P.T2.T1. ~ sub*lag*session, data = df_accuracy_T1T2, FUN = 'mean')
anovaTable$df_accuracy_T1T2 = df_accuracy_T1T2
  
anovakun(df_accuracy_T1T2,"sAB",long=T, peta=T)
PT1T2_anova = forDrawingSigANOVA
PT1T2_anova_post = forDrawingPost

df_accuracy_T1T2$sub = factor(df_accuracy_T1T2$sub ,levels = unique(df_accuracy_T1T2$sub))
df_accuracy_T1T2$lag = factor(df_accuracy_T1T2$lag,levels = unique(df_accuracy_T1T2$lag))
df_accuracy_T1T2$session = factor(df_accuracy_T1T2$session,levels = unique(df_accuracy_T1T2$session))

bf_table = anovaBF(P.T2.T1. ~ lag*session + sub, data=df_accuracy_T1T2, whichRandom = "sub",progress=FALSE)
anovaTable$bf_table=bf_table


config$line=F
config$label_y="Accuracy(T2|T1)"
config$label_y="Lag"
p_all$accuracy_T2T1 = dispLineGraph(df_accuracy_T1T2,config,"P.T2.T1.",c('lag',"session"))+
  geom_line(data = psy_data, 
            aes(x=x,y=y,group=session))+
  theme(
    legend.position = c(0,1),
    legend.justification = c(0,1)
  )



config$ylim = round(seq(0,1,0.2),2)
config$ylim_stride = 0.02
config$xlim = round(seq(1,5,1),2)
config$xlim_stride = 0.5

p_all$accuracy_T2T1 = setEmptyStyle(p_all$accuracy_T2T1,config)
p_all$accuracy_T2T1$size = c(8,10)


df_accuracy_T1T2 = df
df_accuracy_T1T2 = df_accuracy_T1T2[df_accuracy_T1T2$condition=="Both",]
# df_accuracy_T1T2$target = g3[df_accuracy_T1T2$target]

df_accuracy_T1T2 = aggregate(P.T2.T1. ~ sub*lag*session, data = df_accuracy_T1T2, FUN = 'mean')

df_diff = df_accuracy_T1T2[df_accuracy_T1T2$session=="T1-passive",]
df_diff$P.T2.T1.=df_diff$P.T2.T1.-df_accuracy_T1T2[df_accuracy_T1T2$session=="T1-active",]$P.T2.T1.

m <- lmer( P.T2.T1. ~ lag + (1| sub), data = df_diff)

sm = summary(m)
coef_df <- extract_coef_info(sm, c("lag"))
    
intercept = sm$coefficients["(Intercept)", "Estimate"]

lag_vals <- seq(1, 5, by = 0.1)

ribbon_df = data.frame(
  lag = lag_vals,
  y = intercept + sm$coefficients["lag", "Estimate"] * lag_vals,
  ymin = intercept- sm$coefficients["(Intercept)", "Std. Error"] + sm$coefficients["lag", "Estimate"] * lag_vals,
  ymax = intercept + sm$coefficients["(Intercept)", "Std. Error"] + sm$coefficients["lag", "Estimate"] * lag_vals
)

config$grCol=NULL
p_all$accuracy_T2T1_diff = dispLineGraph(df_diff,config,"P.T2.T1.",c('lag'))+
  geom_abline(intercept = intercept,
              slope = sm$coefficients["lag", "Estimate"], size = 0.5,color="black")+
  geom_ribbon(data = ribbon_df, aes(x = lag, y=y,ymin = ymin, ymax = ymax), inherit.aes = FALSE,alpha = 0.2)+
   theme(
    legend.position = 'none'
  )
config$ylim = round(seq(0,0.2,0.05),2)
config$ylim_stride = 0.01
config$xlim = round(seq(1,5,1),2)
config$xlim_stride = 0.5

p_all$accuracy_T2T1_diff = setEmptyStyle(p_all$accuracy_T2T1_diff,config)
p_all$accuracy_T2T1_diff$size = c(8,10)



```

## Results
## Baseline Pupil size
### load data
```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

df_pupil <- load_json_dataframe0(folderName,  paste0("df_pupil.json"))
df <- load_json_dataframe0(folderName, paste0("df",bpass,".json"))
df_event_BP <- load_json_dataframe0(folderName, paste0("df_event_BP",bpass,".json"))

g = NULL
for(iTime in sort(unique(df_event_BP$bin))){
  if (iTime >=0){
    g = rbind(g,paste0(iTime,'-',iTime+1))
  }
}
df_event_BP$bin = g[df_event_BP$bin+1]

```

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

g = c("miss","hit")

# df_pupil = df_pupil[df_pupil$session=="T1-active",]
df_pupil$data_x = df_pupil$Time
df_pupil$sdt = g[df_pupil$P.T2.T1.+1]

config$label_x="Time from T2 onset[s]"
config$label_y="Pupil size[mm]"
config$linetype=F
config$grCol=c('#d97168','gray')

p_all$pupil = disp(df_pupil, config, "pupil", T, c("session","sdt"))+
  geom_vline(xintercept = 0, linetype = "solid", color = "black") +
  facet_wrap(. ~session)

config$ylim = round(seq(4.8,5.6,0.2),2)
config$ylim_stride = 0.02
config$xlim = round(seq(-3,3,1),2)
config$xlim_stride = 0.1

p_all$pupil = setEmptyStyle(p_all$pupil,config)+
  scale_x_continuous(breaks = config$xlim)

p_all$pupil$size=c(10,5)

```

### pupil hit vs. miss
```{r, message=FALSE, echo=FALSE,warning=FALSE,include=FALSE}

mmName = c('miss','hit')

df_accuracy = df
df_accuracy = df_accuracy[df_accuracy$condition=="Both",]
df_accuracy$label = mmName[df_accuracy$P.T2.T1.+1]

df_accuracy = aggregate(PD ~ sub*session*label, data = df_accuracy, FUN = 'mean')

anovakun(df_accuracy,"sAB",long=T, peta=T)
anova_BP = forDrawingSigANOVA
anovaTable$anova_BP=anova_BP

df_accuracy$sub = factor(df_accuracy$sub,levels = unique(df_accuracy$sub))
df_accuracy$session = factor(df_accuracy$session ,levels = unique(df_accuracy$session))
df_accuracy$label = factor(df_accuracy$label,levels = unique(df_accuracy$label))

bf_table_BP = anovaBF(PD ~ session*label+sub, data=df_accuracy, whichRandom = "sub",progress=FALSE)
anovaTable$bf_table_BP=bf_table_BP

# showAnovaSummary(forDrawingSigANOVA,bf_table,4,1)

annotation_df=NULL
ttest_BP=NULL
xpos=1
for (iSession in unique(df_accuracy$session)){
  
  x1 = df_accuracy[(df_accuracy$session==iSession)&(df_accuracy$label=="miss"),]$PD
  x2 = df_accuracy[(df_accuracy$session==iSession)&(df_accuracy$label=="hit"),]$PD
  
  ttest = getTtestSummary(x1,x2)
  ttest_BP[[iSession]] = getTtestSummary(x1,x2)
  
  if( ttest$ttest$p.value < 0.05){
    l = "*"
  }else if ((ttest$ttest$p.value > 0.05)&(ttest$ttest$p.value < 0.1)){
    l = "+"
  }else{ 
    l = "n.s."
  }
  
  annotation_df = rbind(annotation_df,
                        data.frame(
                          session=iSession,
                          x_position = xpos,
                          y_position = mean(x1)+sd(x1)/sqrt(length(unique(df_accuracy$sub))),
                          label = l,
                          pVal=ttest$ttest$p.value
                        ))
  xpos = xpos+1
  
}


config$line=T
config$label_x = ""
config$label_y = "Pupil size[mm]"
config$grCol=rep(c('#d97168','gray'),2)

p_all$PD = dispLineGraph(df_accuracy,config,"PD",c('session',"label"),markerSize=12)+
  geom_text(data = annotation_df, size=7,
            aes(x = x_position, y = y_position, label = label,color=session), inherit.aes = FALSE)+
  theme(
    legend.position = c(1,1),
    legend.justification = c(1,0)
  )


config$ylim = round(seq(4.8,5.4,0.1),2)
config$ylim_stride = 0.02
config$xlim = round(seq(1,2,1),2)
config$xlim_stride = 0.5

p_all$PD = setEmptyStyle(p_all$PD,config)
p_all$PD$size=c(10,10)

mmName = c('miss','hit')

df_accuracy = df
df_accuracy = df_accuracy[df_accuracy$condition=="Both",]
df_accuracy$label = mmName[df_accuracy$P.T2.T1.+1]
df_accuracy = aggregate(PD ~ sub*session*lag*label, data = df_accuracy, FUN = 'mean')
config$title=""
p = dispLineGraph(df_accuracy,config,"PD",c('session',"label","lag"))+
  facet_wrap(.~lag)

```

### pupil bin
```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

df_accuracy = df
df_accuracy = df_accuracy[df_accuracy$condition=="Both",]
# df_accuracy$label = mmName[df_accuracy$P.T2.T1.+1]
# df_accuracy$y = df_accuracy$P.T2.T1.
df_accuracy$PD_bin = df_accuracy$PD_bin+1
df_accuracy$y = df_accuracy$y_resid


modelList = c(
  "y ~ PD_bin + (1| sub)"
)

estimateAll = NULL
ribbon_df = NULL
for(iSession in unique(df_accuracy$session)){
  for( m in modelList){
    
    eval(parse(text=paste0(" m <- lmer(", modelList, ", data = df_accuracy[df_accuracy$session==iSession,])")))
    sm = summary(m)
    # print(sm$coefficients)
    terms <- c("PD")
    coef_df <- extract_coef_info(sm, c("PD_bin"))
    
    intercept = sm$coefficients["(Intercept)", "Estimate"]
    coef_df$formula = c(sm$call$formula)
    coef_df$session = iSession
    coef_df$intercept = intercept
    coef_df$slope = sm$coefficients["PD_bin", "Estimate"]
    coef_df$intercept_min = intercept - sm$coefficients["(Intercept)", "Std. Error"]
    coef_df$intercept_max = intercept + sm$coefficients["(Intercept)", "Std. Error"]
    coef_df$x_position = 1.5
    coef_df$y_position = mean(df_accuracy[(df_accuracy$session==iSession)&
                                            (df_accuracy$PD_bin==1),]$y)+0.03
    
    if (coef_df$pVal<0.001){
      coef_df$pVal = 'p<0.001'
    }
    else{
      coef_df$pVal = paste0('p=',round(coef_df$pVal,4))      
    }
    
    estimateAll = rbind(estimateAll,coef_df)
    
    pupil_vals <- seq(1, 5, by = 0.1)
    ribbon_df = rbind(ribbon_df,
                      data.frame(
                        session = iSession,
                        pupil_bin = pupil_vals,
                        y = intercept + sm$coefficients["PD_bin", "Estimate"] * pupil_vals,
                        ymin = intercept- sm$coefficients["(Intercept)", "Std. Error"] + sm$coefficients["PD_bin", "Estimate"] * pupil_vals,
                        ymax = intercept + sm$coefficients["(Intercept)", "Std. Error"] + sm$coefficients["PD_bin", "Estimate"] * pupil_vals
                      ))
    
  }
}

df_accuracy = aggregate(y ~ sub*session*PD_bin, data = df_accuracy, FUN = 'mean')

config$label_x="Pupil bin"
config$label_y="Accuracy"
config$grCol = c("#E69F00","#738CD9")

config$linetype=F
p_all$PD_bin = dispLineGraph(df_accuracy,config,"y",c('PD_bin',"session"),markerSize=12)+
  geom_abline(data=estimateAll,aes(intercept = intercept, slope = slope,color=session), size = 0.5)+
  geom_ribbon(data = ribbon_df, aes(x = pupil_bin, y=y,ymin = ymin, ymax = ymax, fill = session), alpha = 0.2)+
  scale_color_manual(values = c("T1-active" = "#E69F00", "T1-passive" = "#738CD9"))+
  geom_text(data = estimateAll, size=5,
            aes(x = x_position, y = y_position, label = pVal, color=session), inherit.aes = FALSE)+
  theme(
    legend.position = c(1,1),
    legend.justification = c(1,0)
  )

# print(p_all$PD_bin)
config$ylim = round(seq(0.45,0.7,0.05),2)
config$ylim_stride = 0.02
config$xlim = round(seq(1,5,1),2)
config$xlim_stride = 0.5

p_all$PD_bin = setEmptyStyle(p_all$PD_bin,config)
p_all$PD_bin$size=c(10,10)

```

### pupil size at each bin
```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

# config$line=T
# config$label_x = ""
# config$label_y = "Pupil size[mm]"
# config$grCol=NULL
# # rep(c('#d97168','gray'),2)
# 
# p_all$event_BP = dispLineGraph(df_event_BP,config,"BP",c('bin',"event"),markerSize=12)+
#   # geom_point(data=df_event_BP,aes(x=bin,group=sub,color=order),size = 1,alpha=0.5)+
#   # geom_line(data=df_event_BP,aes(x=bin,group=sub,color=marker),size = 0.5,alpha=0.5)+
#   theme(
#     legend.position = c(1,1),
#     legend.justification = c(1,0)
#   )
# 
# 
# config$ylim = round(seq(4.7,5.5,0.1),2)
# config$ylim_stride = 0.02
# config$xlim = round(seq(1,5,1),2)
# config$xlim_stride = 0.5
# 
# p_all$event_BP = setEmptyStyle(p_all$event_BP,config)
# p_all$event_BP$size=c(10,10)
# 
# anovakun(df_event_BP,"sAB",long=T, peta=T)
# 
# x1 = df_event_BP[(df_event_BP$bin=="2-3")&(df_event_BP$event=="peaks"),]$BP
# x2 = df_event_BP[(df_event_BP$bin=="2-3")&(df_event_BP$event=="troughs"),]$BP
# 
# ttest_1back = getTtestSummary(x1,x2)
# 
# df_event_BP$bin <- factor(df_event_BP$bin, levels = unique(df_event_BP$bin))

p_all$event_BP = dispLineGraph(df_event_BP, config, "BP", c("event","bin"), markerSize=8) +
  facet_grid(. ~ bin)+
  geom_point(
    data = df_event_BP,
    aes(x = event, y = BP, group = sub, color = event),
    position = position_dodge(width = 0.1),
    size = 1, alpha = 0.5,
    inherit.aes = FALSE
  ) +
  geom_line(
    data = df_event_BP,
    aes(x = event, y = BP, group = sub, color = event),
    # position = position_dodge(width = 0.1),
    linewidth = 0.5, alpha = 0.5,
    inherit.aes = FALSE
  ) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 30, hjust = 1)
  )

  
```


## Accuracy
### load data
```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

df <- load_json_dataframe0(folderName, paste0("df",bpass,".json"))
df_sum <- load_json_dataframe0(folderName, paste0("df_sum",bpass,".json"))

```

## Pupil wave
### load data
```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

# df <- load_json_dataframe0(folderName, "df.json")
df <- load_json_dataframe0(folderName, paste0("df2",bpass,".json"))
df_sum <- load_json_dataframe0(folderName,paste0("df_sum",bpass,".json"))
df_pupilTimeCourse <- load_json_dataframe0(folderName,paste0("df_pupilTimeCourse.json"))

g = NULL
for(iTime in sort(unique(df$time_bin))){
  if (iTime >=0){
    g = rbind(g,paste0(iTime,'-',iTime+1))
  }
}

eTime = 6

df_accuracy = df
df_accuracy = df_accuracy[df_accuracy$wave_onset_troughs_st >= 0,]
df_accuracy = df_accuracy[df_accuracy$wave_onset_troughs_st < eTime,]

p <- ggplot(df_accuracy, aes(x = wave_onset_troughs_st, fill = session)) +
  geom_histogram(
    aes(y = after_stat(count / sum(count))),
    bins = 100,
    position = "identity",
    alpha = .6
  ) +
  scale_fill_manual(values = config$grCol) 


```

### Averaged accuracy diff
```{r, message=FALSE, echo=FALSE,warning=FALSE,include=FALSE}

annotation_df_wave=NULL

xlims=NULL
xlims$troughs$ylim=round(seq(0,0.4,0.1),2)
xlims$troughs$ylim_stride=0.01
xlims$peaks$ylim=round(seq(-0.4,0,0.1),2)
xlims$peaks$ylim_stride=0.01

for(phaseType in c('peaks','troughs')){
  annotation_df_wave[[phaseType]]=NULL

  time=df[[paste0("wave_onset_",phaseType,"_st")]]
  for(iTime in 0:eTime){
    df[(time>=iTime)&(time<iTime+1),]["time_bin"]=iTime
  }
  
  df_accuracy = df
  df_accuracy = df_accuracy[df_accuracy$time_bin >= 0,]
  df_accuracy = df_accuracy[df_accuracy$time_bin < eTime,]
  df_accuracy$y = df_accuracy$y_resid_smooth_norm
  # df_accuracy = aggregate(y_resid_smooth_norm ~ sub*time_bin*session, data = df_accuracy, FUN = 'mean')
  df_accuracy = aggregate(y ~ sub*time_bin*session, data = df_accuracy, FUN = 'mean')
  
  for (iTime in unique(df_accuracy$time_bin)){
    for (iSession in unique(df_accuracy$session)){
      
      x1 = df_accuracy[(df_accuracy$time_bin==iTime)&(df_accuracy$session==iSession),]$y
      x2 = rep(0, length(x1))
      
      ttest_1back = getTtestSummary(x1,x2)
      
      if( ttest_1back$ttest$p.value < 0.05){
        l = "*"
      }else if ((ttest_1back$ttest$p.value > 0.05)&(ttest_1back$ttest$p.value < 0.1)){
        l = "+"
      }else{ 
        l = ""
      }
      
      annotation_df_wave[[phaseType]] = rbind(annotation_df_wave[[phaseType]],
                            data.frame(
                              phaseType=phaseType,
                              time_bin = iTime+1,
                              session = iSession,
                              x_position = iTime+1,
                              y_position = mean(x1)+0.025,
                              label = l,
                              pVal=ttest_1back$ttest$p.value,
                              descrip=showTtestSummary(getTtestSummary(x1,x2))
                            ))
      
    }
  }
  
  config$grCol = c("#E69F00","#738CD9")
  
  # config$grCol = NULL
  config$line = T
  config$title = ""
  config$label_x = "Time bin [s]"
  config$label_y = "Accuracy diff. from mean"
  
  df_accuracy$time_bin = g[df_accuracy$time_bin+1]
  df_accuracy$time_bin = factor(df_accuracy$time_bin,levels = g)
  
  p = dispLineGraph(df_accuracy,config,"y",c('time_bin','session'))+
    geom_hline(yintercept = 0, linetype = "solid", color = "black") +
    geom_text(data = annotation_df_wave[[phaseType]], size=7,
              aes(x = x_position, y = y_position, label = label,color=session), inherit.aes = FALSE)+
    theme(
      legend.position = c(1, 1),
      legend.justification = c(1, 1),
      axis.text.x = element_text(angle = 30, hjust = 0.8)
    )
  
  config$ylim = round(seq(-0.15,0.15,0.05),2)
  config$ylim_stride = 0.01
  config$xlim = round(seq(1,eTime,1),2)
  config$xlim_stride = 0.5
  
  p = setEmptyStyle(p,config,size_font=60)
  p$size = c(8,6)
  
  p_all[[paste0("wave_",phaseType)]] = p
  
  
  df_pupilTimeCourse$data_x = df_pupilTimeCourse$Time
  
  config$label_x="Time from pupil constriction[s]"
  config$label_y="Pupil size change[%]"
  config$linetype=F
  p = disp(df_pupilTimeCourse, config, paste0("pupil_",phaseType), T, c("Session"))+
    theme(
      legend.position = c(0,1),
      legend.justification = c(0,1)
    )
  
  
  # config$ylim = round(seq(0,6,2),2)
  config$ylim = xlims[[phaseType]]$ylim
  config$ylim_stride = 0.01
  config$xlim = round(seq(0,6,1),2)
  config$xlim_stride = 0.5
  
  p = setEmptyStyle(p,config,size_font=60)+
    scale_x_continuous(breaks = config$xlim)
  
  p$size=c(8,5)
  
  p_all[[paste0("pupil_",phaseType)]] = p
  
  
}

```

```{r, message=FALSE, echo=FALSE,warning=FALSE}

# df_accuracy = df
# 
# df_accuracy = df_accuracy[df_accuracy$time_bin >= 0,]
# df_accuracy = df_accuracy[df_accuracy$time_bin < eTime,]
# 
# # df_accuracy = df_accuracy[df_accuracy$target == 4,]
# 
# df_accuracy$y = df_accuracy$P.T2.T1._smooth_norm
# # df_accuracy$y = df_accuracy$y_resid_smooth_norm
# 
# df_accuracy = aggregate(y ~ sub*time_bin, data = df_accuracy, FUN = 'mean')
# # df_accuracy = aggregate(P.T2.T1. ~ sub*time_bin, data = df_accuracy, FUN = 'mean')
# # df_accuracy$y_resid_smooth_norm = df_accuracy$P.T2.T1.
# 
# annotation_df=NULL
# for (iTime in unique(df_accuracy$time_bin)){
#   
#   x1 = df_accuracy[(df_accuracy$time_bin==iTime),]$y
#   x2 = rep(0, length(x1))
#   
#   ttest_1back = getTtestSummary(x1,x2)
#   
#   if( ttest_1back$ttest$p.value < 0.05){
#     l = "*"
#   }else if ((ttest_1back$ttest$p.value > 0.05)&(ttest_1back$ttest$p.value < 0.1)){
#     l = "+"
#   }else{ 
#     l = ""
#   }
#   
#   annotation_df = rbind(annotation_df,
#                         data.frame(
#                           time_bin = iTime+1,
#                           x_position = iTime+1,
#                           y_position = mean(x1)+0.025,
#                           label = l,
#                           pVal=ttest_1back$ttest$p.value
#                         ))
#   
# }
# 
# df_accuracy$time_bin = g[df_accuracy$time_bin+1]
# df_accuracy$time_bin = factor(df_accuracy$time_bin,levels = g)
# 
# config$grCol=NULL
# p_all$wave2 = dispLineGraph(df_accuracy,config,"y",c('time_bin'))+
#   geom_hline(yintercept = 0, linetype = "solid", color = "black")+
#   geom_text(data = annotation_df, size=7,
#             aes(x = x_position, y = y_position, label = label), inherit.aes = FALSE)+
#   theme(
#     legend.position = 'none'
#   )
# 
# 
# config$ylim = round(seq(-0.15,0.15,0.05),2)
# config$ylim_stride = 0.01
# config$xlim = round(seq(1,eTime,1),2)
# config$xlim_stride = 0.5
# 
# p_all$wave2 = setEmptyStyle(p_all$wave2,config,size_font=60)
# # scale_x_continuous(breaks = config$xlim)
# 
# # print(p)
# 
# p_all$wave2$size = c(8,6)


```

### Heatmap
```{r, message=FALSE, echo=FALSE,warning=FALSE}

for(phaseType in c('peaks','troughs')){
  
  time=df[[paste0("wave_onset_",phaseType,"_st")]]
  for(iTime in 0:eTime){
    df[(time>=iTime)&(time<iTime+1),]["time_bin"]=iTime
  }
  
  df_accuracy = df
  df_accuracy = df_accuracy[df_accuracy$time_bin >= 0,]
  df_accuracy = df_accuracy[df_accuracy$time_bin < eTime,]
  
  # df_accuracy$y = df_accuracy$P.T2.T1._smooth_norm
  df_accuracy$y = df_accuracy$y_resid_smooth_norm
  
  df_accuracy = aggregate(y ~ time_bin*lag*session, data = df_accuracy, FUN = 'mean')
  df_accuracy$time_bin = g[df_accuracy$time_bin+1]
  df_accuracy$time_bin = factor(df_accuracy$time_bin,levels = g)
  
  for(iSession in unique(df_accuracy$session)){
    
    p = ggplot(df_accuracy[df_accuracy$session==iSession,], 
               aes(x = time_bin, y = lag,fill=y)) +
      geom_tile(color = "white") +
      scale_fill_distiller(palette = "RdBu", direction = -1)+
      scale_fill_gradient2(
        low = "#2C3E94",
        mid = "white",
        high = "#B22222",
        midpoint = 0,
        name = "Accuracy diff. from mean",
        limits = c(-0.3, 0.3)
      )+
      theme_minimal()+
      xlab("Time[s]")+ylab("Lag")+
      guides(fill = guide_colorbar(
        barwidth = 1,
        barheight = 20,
        title.position = "right",
        title.theme = element_text(angle = -90)
      ))+
      theme(
        axis.text.x = element_text(angle = 30, hjust = 0.8)
      )
    config$ylim = round(seq(1,5,1),2)
    config$ylim_stride = 0.1
    config$xlim = round(seq(0,eTime,1),2)
    config$xlim_stride = 0.1
    config$title = iSession
    
    p = setEmptyStyle(p,config,size_font=60)+
      # scale_x_continuous(breaks = g[1:eTime])+
      coord_fixed()+
      ggtitle(iSession)
    
    # print(p)
    p$size=c(8,6)
    p_all[[paste0("heatmap_wave_",phaseType,'_',gsub("-", "_", iSession))]]=p
    
  }
}

```

## Combine figs
```{r, message=FALSE, warning=FALSE, echo=FALSE}

p_all$tmp_fig0_1 = combineGraphs2(c("accuracy_T2T1_diff","accuracy_T2T1"),p_all,c(2,1),c(1,2))
p_all$tmp_fig0_2 = combineGraphs2(c("accuracy_T1","accuracy_T2"),p_all,c(2,1),c(1,1))

p_all$Figure1 = combineGraphs2(c("accuracy_T1","accuracy_T2","tmp_fig0_1"),p_all,c(1,3),c(2,1,4))
p_all$Figure1$size_mm = c(figsize_w,figsize_w)

p_all$Figure2 = combineGraphs2(c("pupil","PD","PD_bin"),p_all,c(1,3),c(3,1,2))
p_all$Figure2$size_mm = c(figsize_w,200)

p_all$tmp_fig2_1 = combineGraphs2(c("pupil_troughs","wave_troughs"),p_all,c(2,1),c(1,2))
p_all$tmp_fig2_2 = combineGraphs2(c("heatmap_wave_troughs_T1_active","heatmap_wave_troughs_T1_passive"),p_all,c(2,1),c(1,1))
# p_all$tmp_fig2$size=c(6,10)

p_all$Figure3 = combineGraphs2(c("tmp_fig2_1","tmp_fig2_2"),p_all,c(1,2),c(1,1))
p_all$Figure3$size_mm = c(figsize_w,figsize_w)

p_all$tmp_fig3_1 = combineGraphs2(c("pupil_peaks","wave_peaks"),p_all,c(2,1),c(1,2))
p_all$tmp_fig3_2 = combineGraphs2(c("heatmap_wave_peaks_T1_active","heatmap_wave_peaks_T1_passive"),p_all,c(2,1),c(1,1))
# p_all$tmp_fig2$size=c(6,10)

p_all$SupFigure1 = combineGraphs2(c("tmp_fig3_1","tmp_fig3_2"),p_all,c(1,2),c(1,1))
p_all$SupFigure1$size_mm = c(figsize_w,figsize_w)


```


# Experiment 2
```{r, message=FALSE, echo=FALSE,warning=FALSE,include=FALSE}

expFolder = paste0(rootFolder,"AuditoryAttentionalBlink_realtime/analysis/data")

folderName = list.files(expFolder, full.names=T)
folderName = folderName[length(folderName)]

date = unlist(strsplit(folderName,"/"))
date = date[length(date)]

dataFolder = paste0(expFolder,"AuditoryAttentionalBlink_realtime/data/",date,"/")
saveFolder = paste0("figure/",format(Sys.time(), '%Y%m%d'),"/")

cfg = jsonlite::fromJSON(paste0(folderName,"/cfg.json"))

figcount = 1

sTime = cfg$TIME_START
eTime = cfg$TIME_END
analysisWin = 1
mmFlg = cfg$mmFlag

subFlg = F
nsFlag = T
saveFig = T
blinkFlg = F
normFlg = T

if(!dir.exists(saveFolder)){
  dir.create(saveFolder)
}

g2 = c('1','2','3','4','5')
g2 = c(80,160,240,320,400)

g3 = c('No-target','T1 only','T2 only','Both')
g4 = c('Behavior')

g5 = c('SBP','LBP')

config <- list(lim_x = c(0,1),
               lim_y = c(2,4),
               alpha = 0.1,
               stride = 0.1,
               label_x = "Time [sec]",
               label_y = "Pupil size[a.u.]",
               title = "",
               linetype = T,
               shape=F,
               # grCol = c("#738CD9","#222222")
               # grCol = c("#AB004A","#222222")
               # grCol = c("#E69F00","#738CD9")
               grCol = c('Black','gray')
               
)

```

### load data
```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

df <- load_json_dataframe(folderName, "df.json")
df_pse_thre <- load_json_dataframe0(folderName, "df_pse_thre.json")

```

### T1 response
```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

config$grCol = c("#4c72b0","#c44e52")
config$label_x=""
config$label_y="Accuracy(T1)"

df_accuracy_T1_exp2 = df
df_accuracy_T1_exp2 = df_accuracy_T1_exp2[(df_accuracy_T1_exp2$condition=="T1_only")|(df_accuracy_T1_exp2$condition=="Both"),]

df_accuracy_T1_exp2 = aggregate(hit_t1 ~ sub*condition*analysis, data = df_accuracy_T1_exp2, FUN = 'mean')

p_all$accuracy_T1_exp2 = dispLineGraph(df_accuracy_T1_exp2,config,"hit_t1",c('condition',"analysis"))+
  theme(legend.position = "none")

config$ylim = round(seq(0.86,1,0.02),2)
config$ylim_stride = 0.02
config$xlim = round(seq(1,2,1),2)
config$xlim_stride = 0.5

p_all$accuracy_T1_exp2 = setEmptyStyle(p_all$accuracy_T1_exp2,config)
p_all$accuracy_T1_exp2$size = c(8,10)

stat_t1_exp2=NULL
x1 = df_accuracy_T1_exp2[(df_accuracy_T1_exp2$condition=="T1_only")&(df_accuracy_T1_exp2$analysis=="LBP"),]$hit_t1
x2 = df_accuracy_T1_exp2[(df_accuracy_T1_exp2$condition=="T1_only")&(df_accuracy_T1_exp2$analysis=="SBP"),]$hit_t1

stat_t1_exp2$T1_only = getTtestSummary(x1,x2)

x0 = df_accuracy_T1_exp2[(df_accuracy_T1_exp2$condition=="Both")&(df_accuracy_T1_exp2$analysis=="LBP"),]$hit_t1
x2 = df_accuracy_T1_exp2[(df_accuracy_T1_exp2$condition=="Both")&(df_accuracy_T1_exp2$analysis=="SBP"),]$hit_t1

stat_t1_exp2$Both = getTtestSummary(x1,x2)

  

```

### T2 response
```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

df_accuracy_T2_exp2 = df
df_accuracy_T2_exp2 = df_accuracy_T2_exp2[(df_accuracy_T2_exp2$condition=="T2_only")|(df_accuracy_T2_exp2$condition=="Both"),]

df_accuracy_T2_exp2 = aggregate(hit_t2 ~ sub*condition*analysis, data = df_accuracy_T2_exp2, FUN = 'mean')

config$label_y="Accuracy(T2)"
p_all$accuracy_T2_exp2 = dispLineGraph(df_accuracy_T2_exp2,config,"hit_t2",c('condition',"analysis"))
  # theme(legend.position = "none")

config$ylim = round(seq(0.5,1,0.1),2)
config$ylim_stride = 0.01
config$xlim = round(seq(1,2,1),2)
config$xlim_stride = 0.5

p_all$accuracy_T2_exp2 = setEmptyStyle(p_all$accuracy_T2_exp2,config)
p_all$accuracy_T2_exp2$size = c(8,10)

stat_t2_exp2=NULL
x1 = df_accuracy_T2_exp2[(df_accuracy_T2_exp2$condition=="T2_only")&(df_accuracy_T2_exp2$analysis=="LBP"),]$hit_t2
x2 = df_accuracy_T2_exp2[(df_accuracy_T2_exp2$condition=="T2_only")&(df_accuracy_T2_exp2$analysis=="SBP"),]$hit_t2

stat_t2_exp2$T2_only = getTtestSummary(x1,x2)

x0 = df_accuracy_T2_exp2[(df_accuracy_T2_exp2$condition=="Both")&(df_accuracy_T2_exp2$analysis=="LBP"),]$hit_t2
x2 = df_accuracy_T2_exp2[(df_accuracy_T2_exp2$condition=="Both")&(df_accuracy_T2_exp2$analysis=="SBP"),]$hit_t2

stat_t2_exp2$Both = getTtestSummary(x1,x2)


```

### P(T2|T1) response
```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

df_accuracy_T1T2_exp2 = df
df_accuracy_T1T2_exp2 = df_accuracy_T1T2_exp2[df_accuracy_T1T2_exp2$condition=="Both",]
df_accuracy_T1T2_exp2 = aggregate(y_resid_PD ~ sub*lag_cond*analysis, data = df_accuracy_T1T2_exp2, FUN = 'mean')

anovakun(df_accuracy_T1T2_exp2,"sAB",long=T, peta=T)
anova_PDregressout_exp2 = forDrawingSigANOVA
anovaTable$anova_PDregressout_exp2=anova_PDregressout_exp2

df_accuracy_T1T2_exp2$sub = factor(df_accuracy_T1T2_exp2$sub ,levels = unique(df_accuracy_T1T2_exp2$sub))
df_accuracy_T1T2_exp2$lag_cond = factor(df_accuracy_T1T2_exp2$lag_cond,levels = unique(df_accuracy_T1T2_exp2$lag_cond))
df_accuracy_T1T2_exp2$analysis = factor(df_accuracy_T1T2_exp2$analysis,levels = unique(df_accuracy_T1T2_exp2$analysis))

bf_table_PDregressout_exp2 = anovaBF(y_resid_PD ~ lag_cond*analysis + sub, data=df_accuracy_T1T2_exp2, whichRandom = "sub",progress=FALSE)
anovaTable$bf_table_PDregressout_exp2=bf_table_PDregressout_exp2

df_accuracy_T1T2_exp2 = df
df_accuracy_T1T2_exp2 = df_accuracy_T1T2_exp2[df_accuracy_T1T2_exp2$condition=="Both",]

df_accuracy_T1T2_exp2$n=1

fit = quickpsy(df_accuracy_T1T2_exp2, lag_cond, P.T2.T1., n, 
               grouping = c("analysis"), 
               prob=0.75, 
               bootstrap = "none",
)

psy_data = data.frame(
  analysis = fit$curves$analysis,
  x = fit$curves$x,
  y = fit$curves$y
)

df_accuracy_T1T2_exp2 = aggregate(P.T2.T1. ~ sub*lag_cond*analysis, data = df_accuracy_T1T2_exp2, FUN = 'mean')
# df_accuracy = aggregate(y_resid ~ sub*lag_cond*analysis, data = df_accuracy, FUN = 'mean')

anovakun(df_accuracy_T1T2_exp2,"sAB",long=T, peta=T)
anova_BP_exp2 = forDrawingSigANOVA
anovaTable$anova_BP_exp2=anova_BP_exp2

df_accuracy_T1T2_exp2$sub = factor(df_accuracy_T1T2_exp2$sub ,levels = unique(df_accuracy_T1T2_exp2$sub))
df_accuracy_T1T2_exp2$lag_cond = factor(df_accuracy_T1T2_exp2$lag_cond,levels = unique(df_accuracy_T1T2_exp2$lag_cond))
df_accuracy_T1T2_exp2$analysis = factor(df_accuracy_T1T2_exp2$analysis,levels = unique(df_accuracy_T1T2_exp2$analysis))

bf_table_exp2 = anovaBF(P.T2.T1. ~ lag_cond*analysis + sub, data=df_accuracy_T1T2_exp2, whichRandom = "sub",progress=FALSE)
anovaTable$bf_table_exp2=bf_table_exp2

# df_accuracy = aggregate(P.T2.T1. ~ sub*analysis, data = df_accuracy, FUN = 'mean')
# anovakun(df_accuracy,"sA",long=T, peta=T)

config$line=F
config$label_y="Accuracy(T2|T1)"
config$label_y="Lag"
config$grCol =  c("#4c72b0","#c44e52")

p_all$accuracy_T2T1_exp2 = dispLineGraph(df_accuracy_T1T2_exp2,config,"P.T2.T1.",c('lag_cond',"analysis"),markerSize = 8)+
  geom_line(data = psy_data,
            aes(x=x,y=y,group=analysis))
# +
  # geom_segment(data = df_pse_thre_ave,
  #              aes(x = threshold, xend = threshold),
  #              y = 0, yend = 1, linetype="dashed",size=0.1)+
  # geom_text(data = df_pse_thre_ave, 
  #           aes(x = 3, y = y,
  #               label=paste0('PSE = ',round(threshold, digits = 1))),size = 3) +
  # theme(
  #   legend.position = c(0,1),
  #   legend.justification = c(0,1)
  # )

config$ylim = round(seq(0.3,0.8,0.1),2)
config$ylim_stride = 0.02
config$xlim = round(seq(1,5,1),2)
config$xlim_stride = 0.5

p_all$accuracy_T2T1_exp2 = setEmptyStyle(p_all$accuracy_T2T1_exp2,config)
p_all$accuracy_T2T1_exp2$size = c(8,10)

A <- na.omit(df_pse_thre$threshold_boot[df_pse_thre$analysis=="LBP"])
Bv <- na.omit(df_pse_thre$threshold_boot[df_pse_thre$analysis=="SBP"])

diffs <- replicate(20000, sample(A,1) - sample(Bv,1))
title = paste0("95% CI[",round(quantile(diffs,0.025),3),",",round(quantile(diffs,0.975),3),"]")

p <- ggplot(df_pse_thre, aes(x = threshold_boot, fill = analysis)) +
  geom_histogram(
    aes(y = after_stat(count / sum(count))),
    bins = 100,
    position = "identity",
    alpha = .6
  ) +
  scale_fill_manual(values = config$grCol) +
  xlab("PSE") +
  ylab("Probability") +
  ggtitle(title)+
  theme(legend.justification=c(0,1), legend.position=c(0,1))+
  geom_point(aes(x=mean(df_pse_thre[df_pse_thre$analysis == "SBP",]$thresholds),
                 y=0.05),shape=6,size=6,color=config$grCol[2])+
  geom_point(aes(x=mean(df_pse_thre[df_pse_thre$analysis == "LBP",]$thresholds),
                 y=0.05),shape=6,size=6,color=config$grCol[1])

config$ylim = round(seq(0,0.05,0.01),4)
config$ylim_stride = 0.01
config$xlim = round(seq(2,4,0.5),4)
# config$xlim = round(seq(0,5,1),4)
config$xlim_stride = 0.1

p = setEmptyStyle(p,config)+
  scale_x_continuous(breaks = config$xlim)+
  theme(
    plot.title = element_text(size = 20)
  )

p_all$pseBootstrap = p
p_all$pseBootstrap$size = c(8,8)




df_accuracy_T1T2 = df
df_accuracy_T1T2 = df_accuracy_T1T2[df_accuracy_T1T2$condition=="Both",]

df_accuracy_T1T2 = aggregate(P.T2.T1. ~ sub*lag_cond*analysis, data = df_accuracy_T1T2, FUN = 'mean')

df_diff = df_accuracy_T1T2[df_accuracy_T1T2$analysis=="SBP",]
df_diff$P.T2.T1.=df_diff$P.T2.T1.-df_accuracy_T1T2[df_accuracy_T1T2$analysis=="LBP",]$P.T2.T1.

m <- lmer( P.T2.T1. ~ lag_cond + (1| sub), data = df_diff)

sm = summary(m)
coef_df <- extract_coef_info(sm, c("lag_cond"))
    
intercept = sm$coefficients["(Intercept)", "Estimate"]

lag_vals <- seq(1, 5, by = 0.1)

ribbon_df = data.frame(
  lag = lag_vals,
  y = intercept + sm$coefficients["lag_cond", "Estimate"] * lag_vals,
  ymin = intercept- sm$coefficients["(Intercept)", "Std. Error"] + sm$coefficients["lag_cond", "Estimate"] * lag_vals,
  ymax = intercept + sm$coefficients["(Intercept)", "Std. Error"] + sm$coefficients["lag_cond", "Estimate"] * lag_vals
)

config$grCol=NULL
p_all$accuracy_T2T1_diff = dispLineGraph(df_diff,config,"P.T2.T1.",c('lag_cond'))+
  geom_abline(intercept = intercept,
              slope = sm$coefficients["lag_cond", "Estimate"], size = 0.5,color="black")+
  geom_ribbon(data = ribbon_df, aes(x = lag, y=y,ymin = ymin, ymax = ymax), inherit.aes = FALSE,alpha = 0.2)+
   theme(
    legend.position = 'none'
  )
config$ylim = round(seq(0,0.1,0.025),3)
config$ylim_stride = 0.01
config$xlim = round(seq(1,5,1),2)
config$xlim_stride = 0.5

p_all$accuracy_T2T1_diff = setEmptyStyle(p_all$accuracy_T2T1_diff,config)
p_all$accuracy_T2T1_diff$size = c(8,10)

```



## Baseline Pupil size
### load data
```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

df_pupil <- load_json_dataframe(folderName, "df_pupil.json")

```

### time-course of pupil around T1
```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

g = c("miss","hit")

# df_pupil = df_pupil[df_pupil$session=="T1-active",]
df_pupil$data_x = df_pupil$time
# df_pupil$sdt = g[df_pupil$P.T2.T1.+1]

config$label_x="Time from T2 onset[s]"
config$label_y="Pupil size[mm]"
config$linetype=F
config$grCol=c('#d97168','gray')
config$lim_x=c(-1.2,1.2)
config$lim_y=c(0.1,0.6)
# config$grCol = c("#c44e52")

# p_all$pupil_LBP = disp(df_pupil[df_pupil["analysis"]=="LBP",], config, "PDR_mm", T, c("analysis"))+
#   geom_vline(xintercept = 0, linetype = "solid", color = "black") +
#   facet_wrap(. ~analysis)+
#   theme(legend.position = "none")
# 
# # config$ylim = round(seq(0,0.32,0.08),2)
# config$ylim = round(seq(5.4,6.,0.1),2)
# # config$ylim = round(seq(0.1,0.6,0.1),2)
# config$ylim_stride = 0.01
# config$xlim = round(seq(-1.,1.,0.25),2)
# config$xlim_stride = 0.1
# 
# p_all$pupil_LBP = setEmptyStyle(p_all$pupil_LBP,config)+
#   scale_x_continuous(breaks = config$xlim)
# 
# # p_all$pupil$size=c(10,5)
# 
# config$grCol = c("#4c72b0")

# p_all$pupil_SBP = disp(df_pupil[df_pupil["analysis"]=="SBP",], config, "PDR_mm", T, c("analysis"))+
#   geom_vline(xintercept = 0, linetype = "solid", color = "black") +
#   facet_wrap(. ~analysis)+
#   theme(legend.position = "none")

# config$ylim = round(seq(-0.4,0.2,0.1),2)
# # config$ylim = round(seq(0.1,0.6,0.1),2)
# config$ylim_stride = 0.01



# p_all$pupil_SBP = setEmptyStyle(p_all$pupil_SBP,config)+
#   scale_x_continuous(breaks = config$xlim)

# p_all$pupil$size=c(10,5)

# p_all$pupil = combineGraphs2(c("pupil_LBP","pupil_SBP"),p_all,c(1,2),c(1,1))
# p_all$pupil$size_mm = c(figsize_w/2,231.77)

config$grCol = c("#c44e52","#4c72b0")
p_all$pupil = disp(df_pupil, config, "PDR_mm", T, c("analysis"))+
  geom_vline(xintercept = 0, linetype = "solid", color = "black")
  # facet_wrap(. ~analysis)+
  # theme(legend.position = "none")

config$ylim = round(seq(5.4,6.,0.1),2)
# config$ylim = round(seq(0.1,0.6,0.1),2)
config$ylim_stride = 0.01
config$xlim = round(seq(-1.0,0.5,0.25),2)
config$xlim_stride = 0.1

p_all$pupil = setEmptyStyle(p_all$pupil,config)+
  scale_x_continuous(breaks = config$xlim)

p_all$pupil$size=c(8,10)

df_pupil[df_pupil$time<=0,]

df_pupil_ave = aggregate(. ~ sub*analysis, data = df_pupil[(df_pupil$time<=0.5)&(df_pupil$time>-1),], FUN = 'mean')

x1 = df_pupil_ave[(df_pupil_ave$analysis=="SBP"),]$PDR_mm
x2 = df_pupil_ave[(df_pupil_ave$analysis=="LBP"),]$PDR_mm

anovaTable$ttest_pupil_size_exp2= getTtestSummary(x1,x2)

annotation_df <- data.frame(
  analysis=c("LBP"),
  start = c("LBP"),
  end = c("SBP"),
  y = 5.95,
  label = paste0("p=",round(ttest$ttest$p.value,3))
)

p_all$pupilSize_exp2 = dispLineGraph(df_pupil_ave,config,"PDR_mm",c("analysis"),markerSize = 8)+
  geom_signif(data=annotation_df,
              aes(xmin=start,xmax=end,annotations=label,y_position=y),
              textsize = 5, size=0.2, tip_length = 0.00,family=fontFamily,manual = TRUE)+
  xlab("")
# +
#   geom_point(data=df_pupil_ave,aes(x=analysis,y=PDR_mm,group=sub),size = 1,alpha=0.5)+
#   geom_line(data=df_pupil_ave,aes(x=analysis,y=PDR_mm,group=sub),size = 0.5,alpha=0.5)

config$ylim = round(seq(5.4,6.,0.1),2)
config$ylim_stride = 0.05
config$xlim = round(seq(1,2,1),2)
config$xlim_stride = 0.5

p_all$pupilSize_exp2 = setEmptyStyle(p_all$pupilSize_exp2,config)
p_all$pupilSize_exp2$size=c(3,10)


```

### pupil bin
```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

df_accuracy = df
df_accuracy = df_accuracy[df_accuracy$condition=="Both",]
df_accuracy$PD_bin = df_accuracy$PD_bin+1
df_accuracy$y = df_accuracy$P.T2.T1.
# df_accuracy$y = df_accuracy$y_resid


tmp_df = aggregate( PD ~ sub*analysis, data = df_accuracy, FUN = 'mean')

x1=tmp_df[tmp_df$analysis=="SBP",]$PD
x2=tmp_df[tmp_df$analysis=="LBP",]$PD

merged <- merge(
  tmp_df[tmp_df$analysis=="SBP", ], 
  tmp_df[tmp_df$analysis=="LBP", ],
  by = "sub",
  suffixes = c("_SBP", "_LBP")
)

merged$marker <- ifelse(
  merged$PD_SBP < merged$PD_LBP,
  "SBP",
  "LBP"
)

tmp_df$marker <- "SBP"
tmp_df$marker[tmp_df$sub %in% merged$sub[merged$marker == "LBP"]] <- "LBP"

# p_all$pupilSize_exp2 p= dispLineGraph(tmp_df,config,"PD",c("analysis"),markerSize = 8)
# p_all$pupilSize_exp2 = ggplot(tmp_df,aes(x=analysis, y=PD,group=analysis))+
# geom_boxplot()+
# # ylab("Streak time [s]")+
# geom_point(aes(x=analysis,group=sub),size = 1,alpha=0.5)+
# geom_line(aes(x=analysis,group=sub,color=marker),size = 0.5,alpha=0.5)
# 
# config$ylim = round(seq(3.5,7.5,0.5),2)
# config$ylim_stride = 0.05
# config$xlim = round(seq(1,2,1),2)
# config$xlim_stride = 0.5
# 
# p_all$pupilSize_exp2 = setEmptyStyle(p_all$pupilSize_exp2,config)
# p_all$pupilSize_exp2$size=c(5,10)

ttest = getTtestSummary(x1,x2)
  
modelList = c(
  "y ~ PD_bin + (1| sub)"
)

estimateAll_exp2 = NULL
ribbon_df = NULL
for(iSession in unique(df_accuracy$analysis)){
  for( m in modelList){
    
    eval(parse(text=paste0(" m <- lmer(", modelList, ", data = df_accuracy[df_accuracy$analysis==iSession,])")))
    sm = summary(m)
    # print(sm$coefficients)
    terms <- c("PD")
    coef_df <- extract_coef_info(sm, c("PD_bin"))
    
    intercept = sm$coefficients["(Intercept)", "Estimate"]
    coef_df$formula = c(sm$call$formula)
    coef_df$analysis = iSession
    coef_df$intercept = intercept
    coef_df$slope = sm$coefficients["PD_bin", "Estimate"]
    coef_df$intercept_min = intercept - sm$coefficients["(Intercept)", "Std. Error"]
    coef_df$intercept_max = intercept + sm$coefficients["(Intercept)", "Std. Error"]
    coef_df$x_position = 1.5
    coef_df$y_position = mean(df_accuracy[(df_accuracy$analysis==iSession)&
                (df_accuracy$PD_bin==1),]$y)+0.03
    
    if (round(coef_df$pVal,4)==0){
      coef_df$pVal = 'p<0.001'
    }else{
      coef_df$pVal = paste0('p=',round(coef_df$pVal,4))
    }

    estimateAll_exp2 = rbind(estimateAll_exp2,coef_df)
    
    pupil_vals <- seq(1, 5, by = 0.1)
    ribbon_df = rbind(ribbon_df,
                      data.frame(
                        analysis = iSession,
                        pupil_bin = pupil_vals,
                        y = intercept + sm$coefficients["PD_bin", "Estimate"] * pupil_vals,
                        ymin = intercept- sm$coefficients["(Intercept)", "Std. Error"] + sm$coefficients["PD_bin", "Estimate"] * pupil_vals,
                        ymax = intercept + sm$coefficients["(Intercept)", "Std. Error"] + sm$coefficients["PD_bin", "Estimate"] * pupil_vals
                      ))
    
  }
}

df_accuracy = aggregate(y ~ sub*analysis*PD_bin, data = df_accuracy, FUN = 'mean')

config$label_x="Pupil bin"
config$label_y="Accuracy"
config$grCol = c("#c44e52","#4c72b0")
 

config$linetype=F
p_all$PD_bin_exp2 = dispLineGraph(df_accuracy,config,"y",c('PD_bin',"analysis"),markerSize = 8)+
  geom_abline(data=estimateAll_exp2,aes(intercept = intercept, slope = slope,color=analysis), size = 0.5)+
  geom_ribbon(data = ribbon_df, aes(x = pupil_bin, y=y,ymin = ymin, ymax = ymax, fill = analysis), alpha = 0.2)+
  # scale_color_manual(values = c("SBP" = "#E69F00", "LBP" = "#738CD9"))+
  geom_text(data = estimateAll_exp2, size=5,
          aes(x = x_position, y = y_position, label = pVal, color=analysis), inherit.aes = FALSE)

# print(p_all$PD_bin)
config$ylim = round(seq(0.5,0.7,0.05),2)
config$ylim_stride = 0.02
config$xlim = round(seq(1,5,1),2)
config$xlim_stride = 0.5

p_all$PD_bin_exp2 = setEmptyStyle(p_all$PD_bin_exp2,config)
p_all$PD_bin_exp2$size=c(10,10)

```


### Combine figs
```{r, message=FALSE, warning=FALSE, echo=FALSE}

p_all$SupFigure2 = combineGraphs2(c("accuracy_T1_exp2","accuracy_T2_exp2"),p_all,c(1,2),c(1,1))
p_all$SupFigure2$size_mm = c(figsize_w,200)

p_all$tmp_fig0_1 = combineGraphs2(c("accuracy_T2T1_diff","accuracy_T2T1_exp2"),p_all,c(2,1),c(1,2))


p_all$tmp_fig0_2 = combineGraphs2(c("pupil","pupilSize_exp2"),p_all,c(1,2),c(1,1))

p_all$tmp_fig0_3 = combineGraphs2(c("accuracy_T2T1_exp2","pseBootstrap"),p_all,c(1,2),c(2,1))

p_all$Figure4 = combineGraphs2(c("tmp_fig0_2","accuracy_T2T1_exp2"),p_all,c(1,2),c(2,1))
p_all$Figure4$size_mm = c(figsize_w,200)

```

# Figure
```{r, message=FALSE, echo=FALSE, warning=FALSE, fig.width = 10, fig.height = 5,include=FALSE}

if(saveFig){
  mmName = names(p_all)
  for(iFig in 1:length(mmName)){
    
    if("size" %in% names(p_all[[iFig]])){
      unitName = "in"
      varName = "size"
      
    }else if("size_mm" %in% names(p_all[[iFig]])){
      unitName = "mm"  
      varName = "size_mm"
    }else{
      next
    }
    ggsave(file =paste0(saveFolder,iFig,"_",mmName[iFig],".pdf"),
           plot = p_all[[iFig]],
           width = p_all[[iFig]][varName][[1]][1], 
           height = p_all[[iFig]][varName][[1]][2],
           units = unitName)
    plot(p_all[[iFig]])
    # dev.off()
    
  }
}
```

```{r, message=FALSE, echo=FALSE, warning=FALSE, fig.width = 10, fig.height = 5,include=FALSE}

res <- list(

  dat_exp1 = dat_exp1, 
  dat_exp2 = dat_exp2, 
  df_sub = df_sub,

  # exp1 key objects
  df_accuracy_T1 = df_accuracy_T1,
  df_accuracy_T2 = df_accuracy_T2,
  df_accuracy_T1T2 = df_accuracy_T1T2,
  PT1T2_anova = PT1T2_anova,
  PT1T2_anova_post=PT1T2_anova_post,
  bf_table = bf_table,
  anova_BP = anova_BP,
  bf_table_BP = bf_table_BP,
  ttest_BP = ttest_BP,
  estimateAll = estimateAll,
  annotation_df=annotation_df,
  annotation_df_wave_peaks=annotation_df_wave$peaks,
  annotation_df_wave_troughs=annotation_df_wave$troughs,
  
  # exp2 key objects
  df_accuracy_T1_exp2 = df_accuracy_T1_exp2,
  df_accuracy_T2_exp2 = df_accuracy_T2_exp2,
  anova_BP_exp2 = anova_BP_exp2,
  bf_table_exp2 = bf_table_exp2,
  df_pse_thre = df_pse_thre,
  diffs = diffs,
  estimateAll_exp2 = estimateAll_exp2,

  anovaTable=anovaTable,
  
  stat_t1_exp2_T1_only=stat_t1_exp2$T1_only,
  stat_t1_exp2_T1_both=stat_t1_exp2$Both,
  stat_t2_exp2_T2_only=stat_t2_exp2$T2_only,
  stat_t2_exp2_T1_both=stat_t2_exp2$Both
)

saveRDS(res, "results_objects.rds")
```